Compositional Certified Resource Bounds

### 2015-04-13 paper/main.tex
read limitations section; clarified the part about non-linear ops

Even certain linear programs cannot be analyzed automatically by
$\toolname$, it is usually the case for programs that rely on heap
invariants (like nul-terminated C strings), for programs making
use of non-linear operations (like \code{\%} or \code{*}), or for
programs whose
termination can only be proved by complex path-sensitive reasoning.

>>>>

Even certain linear programs cannot be analyzed automatically by
$\toolname$, it is usually the case for programs that rely on heap
invariants (like nul-terminated C strings), for programs in which
resource usage depends on the result of non-linear operations (like
\code{\%} or \code{*}) in a non-trivial way, or for programs whose
termination can only be proved by complex path-sensitive reasoning.
